Expanding the scope of experimental archaeology using the Perception-Process-Product analytical framework

### 2023-03-07 manuscript/manuscript.Rmd
add some references.
adding some texts.

---
title: "Expanding the scope of experimental archaeology using the Perception-Process-Product analytical framework"
author: 
- Cheng Liu^[Department of Anthropology, Emory University, Atlanta, GA, USA; raylc1996@outlook.com]
abstract: "This paper presents the Perception-Process-Product analytical framework to expand the scope of experimental archaeology. \\par \\textbf{Keywords:} Experimental archaeology; Ethological analysis; Ethnographical analysis; Collaborative knowledge production"
date: "`r Sys.Date()`"
fontsize: 11pt
output: bookdown::pdf_document2
header-includes:
   - \usepackage{textcomp}
   - \usepackage{utopia}
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \usepackage{caption}
   - \captionsetup[figure]{font=scriptsize}
   - \captionsetup[table]{font=scriptsize}
linestretch: 1.5
link-citations: yes
linkcolor: blue
bibliography: bibliography.bib
csl: apa.csl
---

@@

This paper presents the Perception-Process-Product analytical framework to expand the scope of experimental archaeology (**Figure** \@ref(fig:concept)). minimal engineering using raw materials available in the past to demonstrate it is possible to do something.

This part talks about the goal and toolbox of PPP framework, which is understanding the multi-level understanding of variation. the first two p captures different level of variation: EQUIFINALITY [@chami2015].

@@

Variation: why novice is important?

@@

The last step is uploading the data to a open-access repository [@marwick2017]. The building of manufacture can cost.

>>>>

---
title: "Expanding the scope of experimental archaeology using the Perception-Process-Product analytical framework"
author: 
- Cheng Liu^[Department of Anthropology, Emory University, Atlanta, GA, USA; raylc1996@outlook.com]
abstract: "This paper presents the Perception-Process-Product analytical framework that aims to expand the scope of experimental archaeology . \\par \\textbf{Keywords:} Experimental archaeology; Ethological analysis; Ethnographical analysis; Collaborative knowledge production"
date: "`r Sys.Date()`"
fontsize: 11pt
output: bookdown::pdf_document2
header-includes:
   - \usepackage{textcomp}
   - \usepackage{utopia}
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \usepackage{caption}
   - \captionsetup[figure]{font=scriptsize}
   - \captionsetup[table]{font=scriptsize}
linestretch: 1.5
link-citations: yes
linkcolor: blue
bibliography: bibliography.bib
csl: apa.csl
---

@@

This paper presents the Perception-Process-Product analytical framework to expand the scope of experimental archaeology that mainly focuses on the product level (**Figure** \@ref(fig:concept)). It aims to expose the behavioral variability at multiple levels and build the connections. minimal engineering using raw materials available in the past to demonstrate it is possible to do something.

This part talks about the goal and toolbox of PPP framework, which is understanding the multi-level understanding of variation. the first two p captures different level of variation: EQUIFINALITY [@chami2015]. The process level can be dismantled into two parts: 1)the cognitive and physical demands of certain tool-making behavior; 2) the ethological analysis.

@@

Variation: why novice is important? [@hinds1999]

@@

The last step is uploading the data to a open-access repository [@marwick2017]. The building of manufacture can cost [@simon2015; @gilmore2015].
